EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-31 01_intro.tex
AA: Version 2.0 Iterated full text but intro and conclusions. Added a lot of references. Fixed (almost) all comments. Updated figAHM.
taking a pause before attacking intro  + conclusions. 

Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains a
critical challenge, particularly for multi-orbital systems, systems
at low temperatures or endowed with lower symmetry. During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load.

>>>>

Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains a
critical challenge, particularly for multi-orbital systems, systems
at low temperatures or endowed with lower symmetry. During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load. 
\fixme{(Samuele) Numerous exact diagonalization (ED) open-source software packages have been developed by the scientific community addressing the quantum many-body problem, with a strong emphasis on both efficiency and flexibility. Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017_EDLib} and the more recent XDiag~\cite{wietek2025_xdiag}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015_pomerol}; and for fermions coupled with spins, such as H$\Phi$~\cite{KAWAMURA2017_Hphi,Ido2024_Hphiupdate}.

N.B. if added we may want to delete "(ED)" from the next sentence since it is defined here.}
